### 2017-07-07 introduction.tex
working on intro

Today, researchers are increasingly dependent on the ability to store, manage and analyze vast amounts of
data. The data-sets come in varying size, structure and sensitivity. 
In a typical research lab, collaborators from multiple institutions often share data and techniques
for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.

>>>>

While science has long been collaborative and data driven, today, more than ever before, researchers are dependent on the ability to safely store, effectively manage, and quickly analyze vast amounts of
data. Moreover, individual data-sets that are of interest to science and scholarship vary widely in size, often take on heterogeneous structures, and varying levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can vary from user to user and institution to institution.

In a typical research setting, collaborators from multiple institutions often share data and techniques
for analyzing the data. Given the sensitivity of data, the security of the data is a primary concern.
